MLH1 Data Report

### 2018-03-09 Main_Report.rmd
renamed summary to Main_report
small edits to main report

---
title: 'MLH1 data report'
author: "April Peterson"
date: `r format(Sys.time(), ''%d %B, %Y'')`
output:
  pdf_document: default
  html_document: default
---

@@

#### Research Discription
Measure nMLH1 foci per meiotic cell to estimate recombination rate for diverse strains of house mice (rodents). Comparisons the differences in recombination rates across sexes and genetic background to inform models of how meiotic recombination rates evolve. (insert small picture of meixyte)

#### Discription of Report

@@

Aquired microscope cell images are quantified in batches after being anonimzed. The number of MLH1 foci, number of "achiasmate" and asynasped bivalents are quantified. A quality score is given; 1 to 5 (best to worst).

@@

#MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
#MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]
```

Table of the number of mice used and MLH1 stats. (made with kable).

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

@@

>>>>

---
title: 'MLH1 Data Report'
author: "April Peterson"
date: "some date"
output: rmarkdown::github_document
---

@@

#### Research Description
Measure nMLH1 foci per meiotic cell to estimate recombination rate for diverse strains of house mice abd related rodents. Comparison the differences in recombination rates across sexes and genetic background to inform models of how meiotic recombination rates evolve.

#### Description of Report

@@

Cell images are quantified in batches after file names are anonymized. The number of MLH1 foci, number of "achiasmate" and asynasped bivalents are quantified. A quality score is given; 1 to 5 (best to worst).

@@

#MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
#MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]

#MLH1_data <- MLH1_data %>%
#  arrange(category) %>%
#  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

#MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

@@

Table of the mice used and MLH1 stats.
